Array

### 2013-11-19 PAPERS/Report/AdvancedTypes/AdvancedTypes.tex
Fixing the grammar and the examples.

        \hline
        \multicolumn{3}{|c|}{Predicate: \B{Pred}} \\
        \hline
        \multicolumn{3}{c}{\B{Form} \alt \B{Comp}} \\
        \hline
        \multicolumn{3}{|c|}{Boolean formula: \B{Form}} \\
        \hline
        \B{op} & : & \B{BoolOp} \\
        \B{args} & : & seq \B{Pred} \\
        \hline
        \multicolumn{3}{|c|}{Comparison: \B{Comp}} \\
        \hline
        \B{op} & : & \B{RelOp} \\
        \B{arg1}, \B{arg2} & : & \B{Exp} \\
        \hline
        \multicolumn{3}{|c|}{Data type: \B{Type}} \\
        \hline
        \multicolumn{3}{c}{\B{INT} \alt \B{BOOL}\alt}\\
	\multicolumn{3}{c}{\B{Struct} \alt \B{Array}}\\
	\hline
  	\multicolumn{3}{|c|}{Data structure : \B{Struct}} \\
        \hline
	\B{element} & : &  \B{Name}\\
        \B{id} & : & seq \B{Name} \\
	\B{type} & : & seq \B{Type}\\	
        \hline
        \multicolumn{3}{|c|}{Data array : \B{Array}} \\
        \hline
	\B{dec} & : &  seq \B{Vector} \\
	\B{type} & : & seq \B{CSet}\\
	\B{indexes} & : & seq \B{STerm}\\
	\hline
  	\multicolumn{3}{|c|}{Vector : \B{Vector}} \\
        \hline
	\B{elements} & : & seq \B{Expr}\\ 
	\hline
	\multicolumn{3}{|c|}{Concrete set : \B{CSet}} \\
	\hline
	\multicolumn{3}{c}{BOOL \alt NAT \alt NAT$_{1}$ \alt } \\
	\multicolumn{3}{c}{INT \alt B0\_INTERVAL} \\
	\hline
	\multicolumn{3}{|c|}{B0 interval : \B{B0\_INTERVAL}} \\
	\hline
	\B{start} & : & \B{Exp} \\
	\B{end} & : & \B{Exp} \\
	\hline
	\multicolumn{3}{|c|}{Simple term : \B{STerm}} \\
	\hline
	\B{index} & : &  \B{BOOL} \alt \B{INT} \alt \\ 
	& &  \B{Vari} \alt \B{Cons} \\
%	\multicolumn{3}{c}{ \B{BOOL} \alt \B{INT} \alt }\\
%	\multicolumn{3}{c}{ \B{Vari} \alt \B{Cons} }\\
      \end{tabular}
    \end{tabular}
  }
  }
    \caption{Abstract syntax structure of a B implementation.  For each abstract
      syntax element, we give the name of the class (e.g. \B{CaseBr} for a
      branch in a case instruction, and the different attributes of the class),
      or a list of the possible sub-classes (e.g. \B{Inst} for the different
      kinds of instructions).
      Sequence and optional attributes are denoted ``seq'' and ``opt'',
      respectively}
    \label{tab:node-attr}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{rcl}
      \nt{module} & ::= & \ListOf{\nt{item}} \\
      \nt{item} & ::= & \nt{const\_decl} \alt \nt{function\_decl} \alt \nt{type\_def}
      \alt \nt{const\_def} \alt \nt{var\_def} \alt \nt{function\_def} \\
      \nt{const\_decl} & ::= & \nt{name} \llvm{=} \llvm{external} \llvm{constant} \nt{type} \\
      \nt{type\_def} & ::= & \nt{name} \llvm{=} \llvm{type} \nt{type} \\
      \nt{type} & ::= & \llvm{void} \alt \nt{itype} \alt \llvm{\{} \ListOf{\nt{type}} \llvm{\}} \alt \nt{type}\llvm{*} \\
      \nt{const\_def} & ::= & \nt{name} \llvm{=} \llvm{constant} \nt{type} \nt{iliteral} \\
      \nt{var\_def} & ::= & \nt{name} \llvm{=} \llvm{common} \llvm{global} \nt{type} \llvm{zeroinitializer} \\
      \nt{function\_decl} & ::= & \llvm{declare} \nt{type} \nt{name} \llvm{(} \ListOf{\nt{type}} \llvm{)}\\
      \nt{function\_def} & ::= & \llvm{define} \nt{type} \nt{name} \llvm{(} \ListOf{\nt{param}} \llvm{)} \llvm{\{} \ListOf{\nt{block}} \llvm{\}} \\
      \nt{param} & ::= & \nt{type} \nt{name} \\
      \nt{block} & ::= & \nt{lbl} \llvm{:} \ListOf{\nt{inst}} \\
      \nt{inst} & ::=  & \nt{name} \llvm{=} \llvm{alloca} \nt{type} \\
      & \alt & \nt{name} \llvm{=} \lalt \llvm{add} \alt \llvm{sub} \alt \llvm{mul} \alt \llvm{sdiv} \alt \llvm{srem} \ralt \nt{itype} \nt{exp} \llvm{,} \nt{exp} \\
      & \alt & \nt{name} \llvm{=} \llvm{icmp} \lalt \llvm{eq} \alt \llvm{ne} \alt \llvm{sgt} \alt \llvm{sge} \alt \llvm{slt} \alt \llvm{sle} \ralt \llvm{i1} \nt{exp} \llvm{,} \nt{exp}\\
      & \alt & \nt{name} \llvm{=} \llvm{call} \nt{type} \llvm{(} \ListOf{\nt{arg}} \llvm{)} \\
      & \alt & \nt{name} \llvm{=} \llvm{getelementptr} \nt{type} \llvm{*} \nt{exp}\llvm{,} \nt{index}\llvm{,} \nt{index} \\
      & \alt & \nt{name} \llvm{=} \llvm{load} \nt{type} \nt{exp} \\
      & \alt & \llvm{store} \nt{type} \nt{exp}, \nt{type} \llvm{*} \nt{exp} \\
      & \alt & \llvm{br} \llvm{i1} \nt{exp} \llvm{,} \llvm{label} \nt{lbl} \llvm{,} \llvm{label} \nt{lbl} \\
      & \alt & \llvm{br} \llvm{label} \nt{lbl} \\
%       & \alt & \llvm{switch} \nt{type} \nt{exp} \llvm{,} \llvm{branch} \nt{lbl} \llvm{[} \ListOf{\nt{branch}} \llvm{]} \\
      & \alt & \llvm{ret} \lalt \nt{type} \nt{exp} \alt \llvm{void} \ralt \\
      \nt{exp} & ::= & \nt{name} \alt \nt{iliteral} \alt \llvm{getelementptr} \llvm{(} \nt{type} \nt{exp} \llvm{,} \nt{index} \llvm{,} \nt{index} \llvm{)} \\
      \nt{index} & ::= & \nt{itype} \nt{iliteral} \\
      \nt{branch} & ::= & \nt{iliteral} \nt{iliteral} \nt{lbl} \\
      \nt{arg} & ::= & \nt{type} \nt{exp}
    \end{tabular}
  \end{center}
  \caption{Grammar of the target LLVM subset: \nt{itype}, \nt{iliteral}, \nt{lbl}
    and \nt{name} correspond respectively to integer types, integer literals,
    labels and names. Choices are separated by \alt and optionally delimited by
    \lalt and \ralt.  The \ListOf{} superscript denotes a comma-separated list of
    elements of the annotated entity.}
  \label{fig:llvm-grammar}
\end{figure}

@@

The B0 language supports attribution directly between arrays or structure, even though the attribution
must have the same domain type and range type. \VGM{Project Decision: How translate a direct 
attribution between advanced types, for example, arrayA := arrayB ? The Commenc 
uses a function called ``memmove''. }

%TODO to add this restriction in become equals.

@@

\subsubsection{Issues and problems}
\begin{itemize}
	\item Integrate it to report

	:promptfind
\begin{itemize}
	\item Identify the rules that must be updated:
	\begin{itemize}
		\item \textbf{Atomic expression} - getting an element to manipulate.
		\item %TODO - setting a element 
		\item Others involved rules ?

@@

\newpage

@@

\iffalse  % This content is not visible to reader.
A generic example available at repository ProB\footnote{
\url{https://github.com/bendisposto/probparsers/blob/develop/bparser/src/test/resources/parsable/Array.mch}}.

@@

END
\end{minted}
\fi
\subsection{A  simple example and its LLVM-IR}
\footnotesize{
\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
MACHINE
   Array
VARIABLES arr

@@

; <label>:14                                      ; preds = %11
  %15 = load i32* %2, align 4
  %16 = load i32* %1, align 4
  %17 = sext i32 %16 to i64
  %18 = getelementptr  [100 x i32]* @Array__arr, i32 0, i64 %17
  store i32 %15, i32* %18
  br label %19
; <label>:19                                      ; preds = %14, %11, %8, %5, %0
  ret void
}

@@

; <label>:16                                      ; preds = %14, %8
  ret void
}

>>>>

        \hline
        \multicolumn{3}{|c|}{Predicate: \B{Pred}} \\
        \hline
        \multicolumn{3}{c}{\B{Form} \alt \B{Comp}} \\
        \hline
        \multicolumn{3}{|c|}{Boolean formula: \B{Form}} \\
        \hline
        \B{op} & : & \B{BoolOp} \\
        \B{args} & : & seq \B{Pred} \\
        \hline
        \multicolumn{3}{|c|}{Comparison: \B{Comp}} \\
        \hline
        \B{op} & : & \B{RelOp} \\
        \B{arg1}, \B{arg2} & : & \B{Exp} \\
        \hline
        \multicolumn{3}{|c|}{Data type: \B{Type}} \\
        \hline
        \multicolumn{3}{c}{\B{INT} \alt \B{BOOL}\alt}\\
	\multicolumn{3}{c}{\B{Struct} \alt \B{Array}}\\
	\hline
  	\multicolumn{3}{|c|}{Data structure : \B{Struct}} \\
        \hline
	\B{id} & : &  \B{Name}\\
        \B{elements} & : & seq \B{Name} \\
	\B{type} & : & seq \B{Type}\\	
        \hline
        \multicolumn{3}{|c|}{Data array : \B{Array}} \\
        \hline
	\B{dec} & : &  seq \B{Vector} \\
	\B{type} & : & seq \B{CSet}\\
	\B{indexes} & : & seq \B{STerm}\\
	\hline
  	\multicolumn{3}{|c|}{Vector : \B{Vector}} \\
        \hline
	\B{elements} & : & seq \B{Expr}\\ 
	\hline
	\multicolumn{3}{|c|}{Concrete set : \B{CSet}} \\
	\hline
	\multicolumn{3}{c}{BOOL \alt NAT \alt NAT$_{1}$\alt } \\
	\multicolumn{3}{c}{INT \alt B0\_INTERVAL} \\
	\hline
	\multicolumn{3}{|c|}{B0 interval : \B{B0\_INTERVAL}} \\
	\hline
	\B{start} & : & \B{Exp} \\
	\B{end} & : & \B{Exp} \\
	\hline
	\multicolumn{3}{|c|}{Simple term : \B{STerm}} \\
	\hline
	\B{index} & : &  \B{BOOL} \alt \B{INT}\alt \\ 
	& &  \B{Vari} \alt \B{Cons} \\
      \end{tabular}
    \end{tabular}
  }
  }
    \caption{Abstract syntax structure of a B implementation.  For each abstract
      syntax element, we give the name of the class (e.g. \B{CaseBr} for a
      branch in a case instruction, and the different attributes of the class),
      or a list of the possible sub-classes (e.g. \B{Inst} for the different
      kinds of instructions).
      Sequence and optional attributes are denoted ``seq'' and ``opt'',
      respectively}
    \label{tab:node-attr}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{rcl}
      \nt{module} & ::= & \ListOf{\nt{item}} \\
      \nt{item} & ::= & \nt{const\_decl} \alt \nt{function\_decl} \alt \nt{type\_def}
      \alt \nt{const\_def} \alt \nt{var\_def} \alt \nt{function\_def} \\
      \nt{const\_decl} & ::= & \nt{name} \llvm{=} \llvm{external} \llvm{constant} \nt{type} \\
      \nt{type\_def} & ::= & \nt{name} \llvm{=} \llvm{type} \nt{type} \\
      \nt{type} & ::= & \llvm{void} \alt \nt{itype} \alt \llvm{\{} \ListOf{\nt{type}} \llvm{\}} \alt \nt{type}\llvm{*} \\
      \nt{const\_def} & ::= & \nt{name} \llvm{=} \llvm{constant} \nt{type} \nt{iliteral} \\
      \nt{var\_def} & ::= & \nt{name} \llvm{=} \llvm{common} \llvm{global} \nt{type} \llvm{zeroinitializer} \\
      \nt{function\_decl} & ::= & \llvm{declare} \nt{type} \nt{name} \llvm{(} \ListOf{\nt{type}} \llvm{)}\\
      \nt{function\_def} & ::= & \llvm{define} \nt{type} \nt{name} \llvm{(} \ListOf{\nt{param}} \llvm{)} \llvm{\{} \ListOf{\nt{block}} \llvm{\}} \\
      \nt{param} & ::= & \nt{type} \nt{name} \\
      \nt{block} & ::= & \nt{lbl} \llvm{:} \ListOf{\nt{inst}} \\
      \nt{inst} & ::=  & \nt{name} \llvm{=} \llvm{alloca} \nt{type} \\
      & \alt & \nt{name} \llvm{=} \lalt \llvm{add} \alt \llvm{sub} \alt \llvm{mul} \alt \llvm{sdiv} \alt \llvm{srem} \ralt \nt{itype} \nt{exp} \llvm{,} \nt{exp} \\
      & \alt & \nt{name} \llvm{=} \llvm{icmp} \lalt \llvm{eq} \alt \llvm{ne} \alt \llvm{sgt} \alt \llvm{sge} \alt \llvm{slt} \alt \llvm{sle} \ralt \llvm{i1} \nt{exp} \llvm{,} \nt{exp}\\
      & \alt & \nt{name} \llvm{=} \llvm{call} \nt{type} \llvm{(} \ListOf{\nt{arg}} \llvm{)} \\
      & \alt & \nt{name} \llvm{=} \llvm{getelementptr} \nt{type} \llvm{*} 
\nt{exp}\llvm{,} \nt{index}\llvm{,} \ListOf{\nt{index}} \\
      & \alt & \nt{name} \llvm{=} \llvm{load} \nt{type} \nt{exp} \\
      & \alt & \llvm{store} \nt{type} \nt{exp}, \nt{type} \llvm{*} \nt{exp} \\
      & \alt & \llvm{br} \llvm{i1} \nt{exp} \llvm{,} \llvm{label} \nt{lbl} \llvm{,} \llvm{label} \nt{lbl} \\
      & \alt & \llvm{br} \llvm{label} \nt{lbl} \\
%       & \alt & \llvm{switch} \nt{type} \nt{exp} \llvm{,} \llvm{branch} \nt{lbl} \llvm{[} \ListOf{\nt{branch}} \llvm{]} \\
      & \alt & \llvm{ret} \lalt \nt{type} \nt{exp} \alt \llvm{void} \ralt \\
      \nt{exp} & ::= & \nt{name} \alt \nt{iliteral} \alt \llvm{getelementptr} 
\llvm{(} \nt{type} \nt{exp} \llvm{,} \nt{index} \llvm{,} \ListOf{\nt{index}} \llvm{)} \\
      \nt{index} & ::= & \nt{itype} \nt{iliteral} \\
      \nt{branch} & ::= & \nt{iliteral} \nt{iliteral} \nt{lbl} \\
      \nt{arg} & ::= & \nt{type} \nt{exp}
    \end{tabular}
  \end{center}
  \caption{Grammar of the target LLVM subset: \nt{itype}, \nt{iliteral}, \nt{lbl}
    and \nt{name} correspond respectively to integer types, integer literals,
    labels and names. Choices are separated by \alt and optionally delimited by
    \lalt and \ralt.  The \ListOf{} superscript denotes a comma-separated list of
    elements of the annotated entity. }
  \label{fig:llvm-grammar}
\end{figure}

\VGM{To support arrays and structures, I

added only + after index.}

@@

The B0 language supports attribution directly between arrays or structure, even though the attribution
must have the same domain type and range type. \VGM{Project Decision: How translate a direct 
attribution between advanced types, for example, arrayA := arrayB ? The Commenc 
uses a function called ``memmove''.  %TODO to add this restriction in become equals.
 }

@@

\subsubsection{Issues and problems}
\begin{itemize}
	\item To develop support to structures (more easy)
	\item To integrate it in translation.tex
	\item To develop support to copy all  of an advanced types
	\item To identify the rules that must be updated:

@@

@@

%\iffalse  % This content is not visible to reader.
A generic example available at repository ProB\footnote{
\url{https://github.com/bendisposto/probparsers/blob/develop/bparser/src/test/resources/parsable/Array.mch}}. 
This example can be used in approach using imported components.

@@

END
\end{minted}
%\fi
\subsection{A  simple example and its LLVM-IR}
\footnotesize{
\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
MACHINE
   Array
VARIABLES arr

@@

; <label>:14                                      ; preds = %11
  %15 = load i32* %2, align 4
  %16 = load i32* %1, align 4
  %17 = sext i32 %16 to i64
  %18 = getelementptr  [100 x i32]* @Array__arr, i32 0, i64 %17
  store i32 %15, i32* %18
  br label %19
; <label>:19                                      ; preds = %14, %11, %8, %5, %0
  ret void
}
\end{minted}

@@

; <label>:16                                      ; preds = %14, %8
  ret void
}
\end{minted}
